EldersAIR: Main analysis - Blood Pressure Outcomes

### 2021-05-07 fitbit_cleaning.Rmd
fibit data cleaning new interaction analysis

np_clean <- np_joined %>% 
  mutate(date = ymd(date),
         cals_burned = gsub(",", "", cals_burned),
         cals_burned = as.numeric(cals_burned),
         steps = gsub(",", "", steps),
         steps = as.numeric(steps),
         distance = gsub(",", "", distance),
         distance = as.numeric(distance),
         floors = gsub(",", "", floors),
         floors = as.numeric(floors),
         min_sedentary = gsub(",", "", min_sedentary),
         min_sedentary = as.numeric(min_sedentary),
         min_light_act = gsub(",", "", min_light_act),
         min_light_act = as.numeric(min_light_act),
         min_fairly_act = gsub(",", "", min_fairly_act),
         min_fairly_act = as.numeric(min_fairly_act),
         min_very_act = gsub(",", "", min_very_act),
         min_very_act = as.numeric(min_very_act),
         act_cals = gsub(",", "", act_cals),
         act_cals = as.numeric(act_cals),
         area = "NP") %>% 
  rename(fb_file_name = file_name)
```

@@

>>>>

np_clean <- np_joined %>% 
  mutate(date = ymd(date),
         cals_burned = gsub(",", "", cals_burned),
         cals_burned = as.numeric(cals_burned),
         steps = gsub(",", "", steps),
         steps = as.numeric(steps),
         distance = gsub(",", "", distance),
         distance = as.numeric(distance),
         floors = gsub(",", "", floors),
         floors = as.numeric(floors),
         min_sedentary = gsub(",", "", min_sedentary),
         min_sedentary = as.numeric(min_sedentary),
         min_light_act = gsub(",", "", min_light_act),
         min_light_act = as.numeric(min_light_act),
         min_fairly_act = gsub(",", "", min_fairly_act),
         min_fairly_act = as.numeric(min_fairly_act),
         min_very_act = gsub(",", "", min_very_act),
         min_very_act = as.numeric(min_very_act),
         act_cals = gsub(",", "", act_cals),
         act_cals = as.numeric(act_cals),
         area = "NPT") %>% 
  rename(fb_file_name = file_name)
```

@@

elders_fitbit <- read_rds(paste0(file_path, "Output/elders_fitbit_clean.rds")) %>% 
  mutate(area = if_else(area == "NP", "NPT", area))

fitbit_date <- elders_fitbit %>% 
  select(area, adult_id_num, home_winter_id, winter_id, sampling_visit, 
         date, steps, distance:act_cals, cals_burned, fb_file_name) %>% 
  mutate_if(is.character, as.factor) %>% 
  arrange(area, adult_id_num, winter_id, sampling_visit) %>% 
  filter(!is.na(adult_id_num))

summary(fitbit_date)

write_rds(fitbit_date, paste0(file_path, "Output/elders_fitbit_date.rds"))

fitbit_visit <- fitbit_date %>% 
  group_by(area, adult_id_num, winter_id, sampling_visit) %>% 
  mutate_if(is.numeric, sum, na.rm = T) %>% 
  ungroup() %>% 
  distinct(area, adult_id_num, winter_id, sampling_visit, .keep_all = T) %>% 
  select(-date)

summary(fitbit_visit)

write_rds(fitbit_visit, paste0(file_path, "Output/elders_fitbit_visit.rds"))
```

### 2021-05-07 main_analysis_bp.Rmd
fibit data cleaning new interaction analysis

elders_cleaned_dataset_by_visit <- read_rds(paste0(file_path, "Output/elders_cleaned_dataset_by_visit.rds")) 
```

```{r}
analysis_data <- elders_cleaned_dataset_by_visit %>% 
  mutate(treatment = factor(treatment,
                            levels = c("Placebo", "Filter", "Education"),
                            labels = c("Placebo", "Filter", "Education")),
         visit_intervention_diff = round(difftime(sampling_date, intervention_date, 
                                            units = "days"), digits = 0),
         visit_intervention_diff = as.numeric(visit_intervention_diff),
         visit_intervention_diff = if_else(winter_id == 1, 9999,
                                           visit_intervention_diff)) %>% 
  # All but 4 homes (all NPT homes that used Large Filtretes) in the Filter arm used Winix units
  # Filter type isn't really feasible to use in the analysis due to this small sample size
  mutate(treatment_filter_type = as.character(treatment),
         filter_type = as.character(filter_type),
         treatment_filter_type2 = if_else(treatment_filter_type == "Filter", filter_type,
                                         treatment_filter_type),
         treatment_filter_type = factor(treatment_filter_type2,
                                        levels = c("Placebo", "Education",
                                                   "Large Filtrete", "Winix")),
         filter_type = as.factor(filter_type),
         kw_perc_expected = if_else(treatment == "Education", 100, kw_perc_expected)) %>% 
  mutate(treatment = as.character(treatment),
         perc_exp_quart = cut(kw_perc_expected,
                                  breaks = c(0, 25, 46, 71, 1000),
                                  labels = c("0-25 compliance", "25-50 compliance",
                                             "50-75 compliance", "75-100 compliance")),
         perc_exp_quart = as.character(perc_exp_quart),
         filter_compliance = if_else(treatment == "Filter",
                                     perc_exp_quart, 
                                     treatment),
         treatment = factor(treatment,
                            levels = c("Placebo", "Education", "Filter")),
         filter_compliance = factor(filter_compliance,
                                    levels = c("Placebo", "Education",
                                               "0-25 compliance", "25-50 compliance",
                                               "50-75 compliance", "75-100 compliance"))) %>% 
  select(-treatment_filter_type2) 
```

>>>>

analysis_data <- read_rds(paste0(file_path, "Output/elders_cleaned_dataset_by_visit.rds")) 
```
